Reduced MHD Manuscript

### 2024-12-27 Manuscript/Manuscript.tex
Rename
commit

\begin{abstract}

\end{abstract}

@@

\section{MHD Equations of Motion} 
The magnetohydrodynamic (MHD) equations describe the time evolution of a charged fluid's mass density $\rho$, velocity $\bm{v}$, and magnetic field $\bm{B}$ in some spatial domain $Q\subset \mathbb{R}^3$. In this analysis, we fix $Q=D\times S$, the solid 2-torus. We choose poloidal coordinates $x,y\in D$ on the cross-sectional disks, and toroidal coordinate $z \in S$. The poloidal diameter $a$ and outer toroidal circumference $L$ provide characteristic length scales for our system's dynamics.

@@

\begin{align*}
    \frac{\partial\rho}{\partial t} &= -\nabla\cdot (\rho \bm{v}) \\ 
    \rho \frac{\partial \bm{v}}{\partial t} &= \mu_0^{-1} (\nabla\times\bm{B})\times\bm{B} - \nabla p(\rho) 
\end{align*}

>>>>

@@

\section{MHD Equations of Motion} 
The magnetohydrodynamic (MHD) equations describe the time evolution of a charged fluid's mass density $\rho$, velocity $\bm{v}$, and magnetic field $\bm{B}$ in some spatial domain $Q\subset \mathbb{R}^3$. In this analysis, we fix $Q=D^2\times S^1$, the solid 2-torus. We choose poloidal coordinates $x,y\in D^2$ on the cross-sectional discs, and toroidal coordinate $z \in S^1$. The poloidal diameter $a$ and outer toroidal circumference $L$ provide characteristic length scales for our system's dynamics.

@@
